\documentclass[12pt,courier]{navyletter}


\usepackage{designature}

\author{Dennis Evangelista}
\title{Letter of recommendation for Kieren Rudge}
\navysubj{Letter of recommendation for MIDN 3/c Kieren Rudge}
%\navyfiling{}
%\navyserial{}
\date{\today}
%\navymarking{}

\begin{document}
\makedateblock{}

\begin{navyletterheader}
\navyfrom{Assistant Professor Dennis Jose Evangelista\newline Department of Weapons \& Systems Engineering}
\navyto{Summer Research Programs}
\navyskip{}%
\navysubjline%
%\navyskip{}%
%\navyref{refa}{CVN-71 letter Ser 1234, dtd 2 Jan 2016}
%\navyref{refb}{NAVSEA 250-1500-1 Nuclear Welding Manual}
%\navyref{refc}{Bettis letter Ser 5678, dtd 1 Feb 2016}
%\navyencl{encl1}{blah}
\end{navyletterheader}

\section{}
This letter of recommendation is on behalf of MIDN 3/c Kieren Rudge.  Mr.~Rudge was a student in my Introduction to Systems Engineering course, taught to all systems engineering majors during their second year here at the Academy. The course focuses on getting students to think like engineers, as well as learn C programming (on an mbed microcontroller) and Matlab. Mr.~Rudge excelled at all of these and received an A in my class. He has recently been offered a position in the honors program. 

\section{} 
Among his highly competetive group of fellow engineering midshipmen, MIDN 3/c Rudge distinguished himself with outstanding coding and presentation and communication skills.  Working on a team with other midshipmen, he developed a high-sortie-rate paper airplane launcher consisting of two friction wheels and a servo-driven reloading arm controlled by a microcontroller.   He also developed a Street Fighter-like video game with a Naval Academy boxing theme.  Every student here at the Academy is required to study some engineering, and the ones like Mr.~Rudge, who thrive in engineering majors, are as intense as any MIT or Caltech power tool.  

\section{}
Over the term I have known him, I have been impressed by MIDN 3/c Rudge's interest in biomechanics and biomedical engineering.  I believe he would learn much as an undergraduate researcher and make good contributions in a summer research program examining robotics, biomedical engineering, or other medical research.  I only regret I will not be able to host Mr.~Rudge doing summer research on my own research; having worked with undergraduate researchers at MIT, Berkeley, and UNC I believe he shows as much promise as my previous students in those programs.


\noclosing{}\\
\noindent\hspace*{4in}\includesignature{}
\signature{D EVANGELISTA}

%\copyto
%File
\end{document}