\documentclass[12pt,courier]{navyletter}


\usepackage{designature}

\author{Dennis Evangelista}
\title{Letter of recommendation for Kieren Rudge}
\navysubj{Letter of recommendation for MIDN 3/c Kieren Rudge}
%\navyfiling{}
%\navyserial{}
\date{\today}
%\navymarking{}

\begin{document}
\makedateblock{}

\begin{navyletterheader}
\navyfrom{Assistant Professor Dennis Jose Evangelista\newline Department of Weapons \& Systems Engineering}
\navyto{Admissions Board}
\navyskip{}%
\navysubjline%
%\navyskip{}%
%\navyref{refa}{CVN-71 letter Ser 1234, dtd 2 Jan 2016}
%\navyref{refb}{NAVSEA 250-1500-1 Nuclear Welding Manual}
%\navyref{refc}{Bettis letter Ser 5678, dtd 1 Feb 2016}
%\navyencl{encl1}{blah}
\end{navyletterheader}

\section{}
This letter of recommendation is on behalf of MIDN 3/c Kieren Rudge.  Mr.~Rudge was a student in my Introduction to Systems Engineering course, taught to all systems engineering majors during their second year here at the Academy. The course focuses on getting students to think like engineers, as well as learn C programming (on an mbed microcontroller) and Matlab (it would be similar to 10.001 at MIT, with elements from 2.007 and 2.737).   Mr.~Rudge excelled at all of these and received an A in my class.  

\section{} 
Among his highly competetive group of fellow engineering midshipmen, MIDN 3/c Rudge distinguished himself with outstanding coding and presentation and communication skills.  Working on a team with other midshipmen, he developed a high-sortie-rate paper airplane launcher consisting of two friction wheels and a servo-driven reloading arm controlled by a microcontroller.   He also developed a Street Fighter-like video game with a Naval Academy boxing theme.  Every student here at the Academy is required to study some engineering, and the ones like Mr.~Rudge, who thrive in engineering majors, are as intense as any MIT power tool.  

\section{}
Over the term I have known him, I have been impressed by MIDN 3/c Rudge's interest in biomechanics and biomedical engineering.  It is especially bittersweet for me to write this letter for him; my research is in comparative biomechanics and I would have loved to have had Mr. Rudge for a senior capstone project in that topic.  I was Course 6 and Course 2 as an undergrad, and was a TA for 2.001 and 2.005; from personal experience, Mr.~Rudge is as skilled as any second year engineering student from MIT.  I believe he would do very well as a transfer student. 


\noclosing{}\\
\noindent\hspace*{4in}\includesignature{}
\signature{D EVANGELISTA `99}

%\copyto
%File
\end{document}